---
title: Data Dictionary
output: 
  html_document:
    df_print: paged
    code_folding: hide
    code_download: true 
---


```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.align="center")
```

```{r, include=FALSE}
library(readr)
library(readxl)
library(tidyverse)
library(gridExtra)
library(knitr) 
library(kableExtra)
```

## {.tabset .tabset-fade}
```{r include= FALSE}
FIXD71 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-D71")
FIXD72 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-D72")
FIXD73 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-D73")
FIXF11 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-F11")
FIXF12 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-F12")
FIXF13 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-F13")
FIXF13 <- FIXF13[1:137,]
Machine13 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "MACHINE-13")
Machine15 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "MACHINE-15")
```


```{r include=FALSE}
(colnames(FIXD71)==colnames(FIXD72) & colnames(FIXD72)==colnames(FIXD73) & colnames(FIXD73)==colnames(FIXF11) & colnames(FIXF11)==colnames(FIXF12) & colnames(FIXF12)==colnames(FIXF13) & colnames(FIXF12)==colnames(Machine13) & colnames(Machine13)==colnames(Machine15))

((FIXD71[1,])==(FIXD72[1,]) & (FIXD72[1,])==(FIXD73[1,]) & (FIXD73[1,])==(FIXF11[1,]) & (FIXF11[1,])==(FIXF12[1,]) & (FIXF12[1,])==(FIXF13[1,]) & (FIXF13[1,])==(Machine13[1,]) & (Machine13[1,])==(Machine15[1,]) )
```


```{r include=FALSE}
feauture_names <- c(paste0(colnames(FIXD71),"_", FIXD71[1,])) 
feauture_names[1:6]<- c("Part_Desc","Date","Status","Shift","Trim","Fixture_model")
feauture_names <-gsub("-", "_",feauture_names)
```


```{r include= FALSE}
data_process<-function(data_in,text){
   # Rename columns
  DI <- as.data.frame(data_in[5:nrow(data_in),])
  colnames(DI)<- feauture_names
  
  #convert to numeric: ## check that it should not get rounded
  cols = 7:ncol(DI);    
  DI[,cols] = apply(DI[,cols], 2, function(x) as.numeric(as.character(x)))
  
  ## Next Part
  myfunc<-function(x,data_in_cap){
  for (i in x){t= (x<data_in_cap) & (x> -data_in_cap)}
  return(t)
  }
  
  data_in_cap <- as.numeric(data_in[3,7:ncol(data_in)])
  flag_data_in <- data.frame(sweep(DI[,7:ncol(DI)], 2, data_in_cap, "myfunc"))
  
  flagcols = 1:ncol(flag_data_in);    
  flag_data_in[,flagcols] = apply(flag_data_in[,flagcols], 2, function(x) as.numeric(as.logical(x)))
  #all.equal(flag_D71,flag_D71_check)
  
  count_flag_data_in_pass <- colSums(flag_data_in)
  count_flag_data_in_fail <- colSums(!flag_data_in)
  count_flag_data_out <- data.frame(colnames(flag_data_in),count_flag_data_in_pass,count_flag_data_in_fail)
  count_flag_data_out$fixture <- text
  colnames(count_flag_data_out) <- c("feature","pass","fail","fixture_type")
  
  return(count_flag_data_out)
}
```


```{r include= FALSE}
#A) FIXD71
# Rename columns
D71 <- as.data.frame(FIXD71[5:nrow(FIXD71),])
colnames(D71)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(D71);    
D71[,cols] = apply(D71[,cols], 2, function(x) as.numeric(as.character(x)))

count_D71<- data_process(data_in=FIXD71, text = "FIXD71") 
```


```{r include= FALSE}
# B) FIXD72
# Rename columns
D72 <- as.data.frame(FIXD72[5:nrow(FIXD72),])
colnames(D72)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(D72);    
D72[,cols] = apply(D72[,cols], 2, function(x) as.numeric(as.character(x)))

count_D72<- data_process(data_in=FIXD72, text = "FIXD72") 
```



```{r include= FALSE}
#C) FIXD73
# Rename columns
D73 <- as.data.frame(FIXD73[5:nrow(FIXD73),])
colnames(D73)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(D73);    
D73[,cols] = apply(D73[,cols], 2, function(x) as.numeric(as.character(x)))

count_D73<- data_process(data_in=FIXD73, text = "FIXD73") 
```



```{r include= FALSE}
#D) FIXF11
# Rename columns
F11 <- as.data.frame(FIXF11[5:nrow(FIXF11),])
colnames(F11)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(F11);    
F11[,cols] = apply(F11[,cols], 2, function(x) as.numeric(as.character(x)))

count_F11<- data_process(data_in=FIXF11, text = "FIXF11") 
```



```{r include= FALSE}
# E) FIXF12
# Rename columns
F12 <- as.data.frame(FIXF12[5:nrow(FIXF12),])
colnames(F12)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(F12);    
F12[,cols] = apply(F12[,cols], 2, function(x) as.numeric(as.character(x)))

count_F12<- data_process(data_in=FIXF12, text = "FIXF12") 
```



```{r include= FALSE}
#F) FIXF13
#nrow(FIXF13) is 137, others NA values due to formatting
# Rename columns
F13 <- as.data.frame(FIXF13[5:nrow(FIXF13),])
colnames(F13)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(F13);    
F13[,cols] = apply(F13[,cols], 2, function(x) as.numeric(as.character(x)))

count_F13<- data_process(data_in=FIXF13, text = "FIXF13") 
```



```{r include= FALSE}
# G) Machine13
# Rename columns
M13 <- as.data.frame(Machine13[5:nrow(Machine13),])
colnames(M13)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(M13);    
M13[,cols] = apply(M13[,cols], 2, function(x) as.numeric(as.character(x)))

count_M13<- data_process(data_in=Machine13, text = "Machine13") 
```



```{r include= FALSE}
#H) Machine15
# Rename columns
M15 <- as.data.frame(Machine15[5:nrow(Machine15),])
colnames(M15)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(M15);    
M15[,cols] = apply(M15[,cols], 2, function(x) as.numeric(as.character(x)))

count_M15<- data_process(data_in=Machine15, text = "Machine15") 
```


### FIXTURE D71
This dataset contains the parts that are machined by fixture D71 of Machine 13. It has multiple parts that are processed by it, which is represented by its rows. The columns show the nominal value, upper tolerance cap and lower tolerance cap for each feature specification like diameter, flatness cylindricity etc.

It consists of 150 observations + 3 specifications in its rows and 54 feature columns. 

Below is the snippet of the Fixture D71:

```{r message = FALSE,cols.print=10, rows.print=10}
D71
```


Important Variables common for all the  datasets are:


#### {.tabset .tabset-fade}


##### *Diameter*:

* SC01-DIA

* SC03-DIA

* SC05-DIA

* SC07-DIA

* SC08-DIA

* SC09-DIA

* SC16-DIA-1

* SC16-DIA-2

##### *Distance*:

* SC06-DIST	

* SC10-DIST

* SC10-DIST

* SC10-DIST	

* SC13-DIST-1	

* SC13-DIST-2	

* SC13-DIST-3	

* SC13-DIST-4	

* SC15-DIST

* SC05-DIS

##### *Flatness*:

* PLN-A-FLT	

* SC03-FLT	
	
##### *Position coordinates*:	

* SC02-TP-X	

* SC02-TP-Z	

* SC02-TP	

* SC05-TP-X	

* SC05-TP-Z	

* SC05-TP	

* SC05-CYL	

* SC07-TP-X	

* SC07-TP-Z	

* SC07-TP	

* SC08-TP-X-AF	

* SC08-TP-Z-AF	

* SC08-TP-AF	

* SC08-TP-X-ABC	

* SC08-TP-Z-ABC	

* SC08-TP-ABC	

* SC09-TP-X-ABC	

* SC09-TP-Z-ABC	

* SC09-TP-ABC	

* SC09-TP-X-AF	

* SC09-TP-Z-AF

* SC09-TP-AF

* SC16-TP-X	

* SC16-TP-Z	

* SC16-TP	

* SC14-TP-X	

* SC14-TP-Z	

* SC14-TP

##### *Others*:
* SC03-PARA


### FIXTURE D72
This dataset contains the parts that are machined by fixture D72 of Machine 13. It has multiple parts that are processed by it, which is represented by its rows. The columns show the nominal value, upper tolerance cap and lower tolerance cap for each feature specification like diameter, flatness cylindricity etc.

It consists of 98 observations + 3 specifications in its rows and 54 feature columns.  

Below is the snippet of the Fixture D72:

```{r message = FALSE}
D72
```

### FIXTURE D73
This dataset contains the parts that are machined by fixture D73 of Machine 13. It has multiple parts that are processed by it, which is represented by its rows. The columns show the nominal value, upper tolerance cap and lower tolerance cap for each feature specification like diameter, flatness cylindricity etc.

It consists of 125 observations + 3 specifications in its rows and 49 dimensional feature columns + 5 additional information columns.  

Below is the snippet of the Fixture D73:

```{r message = FALSE}
D73
```

### FIXTURE F11
This dataset contains the parts that are machined by fixture F11 of Machine 15. It has multiple parts that are processed by it, which is represented by its rows. The columns show the nominal value, upper tolerance cap and lower tolerance cap for each feature specification like diameter, flatness cylindricity etc.


It consists of 136 observations + 3 specifications in its rows and 49 dimensional feature columns + 5 additional information columns.  

Below is the snippet of Fixture F11 Dataset:

```{r message = FALSE}
F11
```


### FIXTURE F12
This dataset contains the parts that are machined by fixture F12 of Machine 15. It has multiple parts that are processed by it, which is represented by its rows. The columns show the nominal value, upper tolerance cap and lower tolerance cap for each feature specification like diameter, flatness cylindricity etc.

It consists of 112 observations + 3 specifications in its rows and 49 dimensional feature columns + 5 additional information columns.  

Below is the snippet of the Fixture F12:

```{r message = FALSE}
F12
```


### FIXTURE F13
This dataset contains the parts that are machined by fixture F13 of Machine 15. It has multiple parts that are processed by it, which is represented by its rows. The columns show the nominal value, upper tolerance cap and lower tolerance cap for each feature specification like diameter, flatness cylindricity etc.

It consists of 133 observations + 3 specifications in its rows and 49 dimensional feature columns + 5 additional information columns.  

Below is the snippet of the Fixture F13:

```{r message = FALSE}
F13
```


### Machine M13
Aggregated tables: This is a consolidated table of Fixture D71, D72, D73.

```{r message = FALSE}
M13
```


### Machine M15
Aggregated tables: This is a consolidated table of Fixture F11, F12, F13

```{r message = FALSE}
M15
```

