---
title: "Predictive Model for likelihood of Passing the Process Specifications"
output: 
  html_document:
    df_print: paged
    code_folding: hide
    code_download: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## {.tabset .tabset-fade}

### Model Building:

```{r include=FALSE}
### Data Processing:
#Load libraries, clean data, modify columns (convert values to numeric) and rows as needed for analysis:
library(qdapRegex)
library(caret)
library(caTools)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(knitr)
library(stringr)
library(lubridate)
library(readxl)
library(shiny)
library(rsconnect)
library(ggplot2)
library(pROC)
library(ROCR)
```


```{r include= FALSE}
# read import data
FIXD71 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-D71")
FIXD72 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-D72")
FIXD73 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-D73")
FIXF11 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-F11")
FIXF12 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-F12")
FIXF13 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "FIXTURE-F13")
FIXF13 <- FIXF13[1:137,]
Machine13 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "MACHINE-13")
Machine15 <- read_excel("data/Part-Data-Analysis[1].xlsx", sheet = "MACHINE-15")
```


```{r include=FALSE}
## to check if the column features are same for all sheets
(colnames(FIXD71)==colnames(FIXD72) & colnames(FIXD72)==colnames(FIXD73) & colnames(FIXD73)==colnames(FIXF11) & colnames(FIXF11)==colnames(FIXF12) & colnames(FIXF12)==colnames(FIXF13) & colnames(FIXF12)==colnames(Machine13) & colnames(Machine13)==colnames(Machine15))

((FIXD71[1,])==(FIXD72[1,]) & (FIXD72[1,])==(FIXD73[1,]) & (FIXD73[1,])==(FIXF11[1,]) & (FIXF11[1,])==(FIXF12[1,]) & (FIXF12[1,])==(FIXF13[1,]) & (FIXF13[1,])==(Machine13[1,]) & (Machine13[1,])==(Machine15[1,]) )
```


```{r include=FALSE}
feauture_names <- c(paste0(colnames(FIXD71),"_", FIXD71[1,])) 
feauture_names[1:6]<- c("Part_Desc","Date","Status","Shift","Trim","Fixture_model")
feauture_names <-gsub("-", "_",feauture_names)
```


```{r include= FALSE}
# data pre processing function
data_process<-function(data_in,text,flag){
   # Rename columns
  DI <- as.data.frame(data_in[5:nrow(data_in),])
  colnames(DI)<- feauture_names
  
  #convert to numeric: ## check that it should not get rounded
  cols = 7:ncol(DI);    
  DI[,cols] = apply(DI[,cols], 2, function(x) as.numeric(as.character(x)))
  
  ## Next Part
  myfunc<-function(x,data_in_cap){
  for (i in x){t= (x<data_in_cap) & (x> -data_in_cap)}
  return(t)
  }
  
  data_in_cap <- as.numeric(data_in[3,7:ncol(data_in)])
  flag_data_in <- data.frame(sweep(DI[,7:ncol(DI)], 2, data_in_cap, "myfunc"))
  
  flagcols = 1:ncol(flag_data_in);    
  flag_data_in[,flagcols] = apply(flag_data_in[,flagcols], 2, function(x) as.numeric(as.logical(x)))
  #all.equal(flag_D71,flag_D71_check)
  
  ## tabulate out of tolerance failure and passed obs againts all features
  count_flag_data_in_pass <- colSums(flag_data_in)
  count_flag_data_in_fail <- colSums(!flag_data_in)
  count_flag_data_out <- data.frame(colnames(flag_data_in),count_flag_data_in_pass,count_flag_data_in_fail)
  count_flag_data_out$fixture <- text
  colnames(count_flag_data_out) <- c("feature","pass","fail","fixture_type")
  
  if (flag==1) {
    return(flag_data_in)
  }else {
   return(count_flag_data_out) 
  }
}
```


```{r include= FALSE}
#A) FIXD71 : function call to pre processing
# Rename columns
D71 <- as.data.frame(FIXD71[5:nrow(FIXD71),])
colnames(D71)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(D71);    
D71[,cols] = apply(D71[,cols], 2, function(x) as.numeric(as.character(x)))

count_D71<- data_process(data_in=FIXD71, text = "FIXD71",flag=0) 
```


```{r include= FALSE}
# B) FIXD72 : function call to pre processing
# Rename columns
D72 <- as.data.frame(FIXD72[5:nrow(FIXD72),])
colnames(D72)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(D72);    
D72[,cols] = apply(D72[,cols], 2, function(x) as.numeric(as.character(x)))

count_D72<- data_process(data_in=FIXD72, text = "FIXD72",flag=0) 
```



```{r include= FALSE}
#C) FIXD73 : function call to pre processing
# Rename columns
D73 <- as.data.frame(FIXD73[5:nrow(FIXD73),])
colnames(D73)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(D73);    
D73[,cols] = apply(D73[,cols], 2, function(x) as.numeric(as.character(x)))

count_D73<- data_process(data_in=FIXD73, text = "FIXD73",flag=0) 
```



```{r include= FALSE}
#D) FIXF11 : function call to pre processing
# Rename columns
F11 <- as.data.frame(FIXF11[5:nrow(FIXF11),])
colnames(F11)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(F11);    
F11[,cols] = apply(F11[,cols], 2, function(x) as.numeric(as.character(x)))

count_F11<- data_process(data_in=FIXF11, text = "FIXF11",flag=0) 
```



```{r include= FALSE}
# E) FIXF12 : function call to pre processing
# Rename columns
F12 <- as.data.frame(FIXF12[5:nrow(FIXF12),])
colnames(F12)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(F12);    
F12[,cols] = apply(F12[,cols], 2, function(x) as.numeric(as.character(x)))

count_F12<- data_process(data_in=FIXF12, text = "FIXF12",flag=0) 
```



```{r include= FALSE}
#F) FIXF13 : function call to pre processing
#nrow(FIXF13) is 137, others NA values due to formatting
# Rename columns
F13 <- as.data.frame(FIXF13[5:nrow(FIXF13),])
colnames(F13)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(F13);    
F13[,cols] = apply(F13[,cols], 2, function(x) as.numeric(as.character(x)))

count_F13<- data_process(data_in=FIXF13, text = "FIXF13",flag=0) 
```



```{r include= FALSE}
# G) Machine13 : function call to pre processing
# Rename columns
M13 <- as.data.frame(Machine13[5:nrow(Machine13),])
colnames(M13)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(M13);    
M13[,cols] = apply(M13[,cols], 2, function(x) as.numeric(as.character(x)))

count_M13<- data_process(data_in=Machine13, text = "Machine13",flag=0) 
flag_M13 <- data_process(data_in=Machine13, text = "Machine13",flag=1)
```



```{r include= FALSE}
#H) Machine15 : function call to pre processing
# Rename columns
M15 <- as.data.frame(Machine15[5:nrow(Machine15),])
colnames(M15)<- feauture_names

#convert to numeric: ## check that it should not get rounded
cols = 7:ncol(M15);    
M15[,cols] = apply(M15[,cols], 2, function(x) as.numeric(as.character(x)))

count_M15<- data_process(data_in=Machine15, text = "Machine15",flag=0) 
flag_M15 <- data_process(data_in=Machine15, text = "Machine15",flag=1)
```



```{r include=FALSE}
flag_M13$Machine <- "Machine_13"
flag_M15$Machine <- "Machine_15"

flag_M13 <- flag_M13[c(50,1:49)]
flag_M15 <- flag_M15[c(50,1:49)]


flag_M13 <- cbind(M13[,1:6],flag_M13) %>% 
            as.data.frame() %>% 
            mutate(part_names = as.character(rm_between(Part_Desc, ":", ":", extract=TRUE)))

flag_M15 <- cbind(M15[,1:6],flag_M15) %>% 
            as.data.frame() %>% 
            mutate(part_names = as.character(rm_between(Part_Desc, ":", ":", extract=TRUE)))

flag_M13 <- flag_M13[c(1,57,2:56)]
flag_M15 <- flag_M15[c(1,57,2:56)]
```


```{r include=FALSE}
flag_M13_gather <-flag_M13 %>% gather("dimensional_feature","pass_flag",9:57)
flag_M15_gather <-flag_M15 %>% gather("dimensional_feature","pass_flag",9:57)
flag_machines <-rbind(flag_M13_gather,flag_M15_gather)
```

Logit on Likelihood to pass:

1. set seed and split into train and test
```{r include=FALSE}
## 75% of the sample size
smp_size <- floor(0.75 * nrow(flag_machines))

## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(flag_machines)), size = smp_size)

train <- flag_machines[train_ind, ]
test <- flag_machines[-train_ind, ]
```

2. Train Logistic Regression Model
```{r include=FALSE}
#logistic regression model
model <- glm (pass_flag ~ .-Part_Desc, data = train, family = binomial)
```


The Table might seem long, to view the prediction results, please move to the adjacent tabs.
```{r}
summary(model)
```

### Evaluate on Training Data:
3. Predict on Train
```{r include=FALSE}
predict <- predict(model, type = 'response')
```

4. Check Confusion Matrix:
      
      From the below table we can say that, the model predicted fail for 2460/ 27709 observations, out of which 1498 were       correct predictions and 962 were false negatives. 
      
      Also, the model predicted pass for 25249 observations of which 24659 were correctly predicted and 590 are false           positives. 
      
      
```{r}
#confusion matrix
table(train$pass_flag, predict > 0.5) %>% kable()
```




5. ROC Curve: The Higher the Area under the curve, better is the model.
```{r}
#ROCR Curve
ROCRpred <- prediction(predict, train$pass_flag)
ROCRperf <- performance(ROCRpred, 'tpr','fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2,1.7))
```



6. AUC Training: 93.21%
```{r}
roc_obj <- roc(train$pass_flag, predict)
auc(roc_obj)
```


7. Measure Model Accuracy on taining data:
```{r}
fitted.results <- ifelse(predict > 0.5,1,0) %>% as.factor()
cm<-confusionMatrix(data=fitted.results, 
  reference=as.factor(train$pass_flag))

Accuracy<-round(cm$overall[1],2)
```
        
        Hence the accuracy of this base model is :
        
        Accurary = (True Positives +True Negatives)/Total = `r round(Accuracy*100,2)` %


```{r include=FALSE}
#7. Add probability to pass as a column in training data:
train$predicted <- predict
```





### Evaluate on Test Data:

3. Predict on Test
```{r include=FALSE}
predict <- predict(model,newdata=test, type = 'response')
```

4. Check Confusion Matrix
```{r}
#confusion matrix
table(test$pass_flag, predict > 0.5)%>% kable()
```


5. ROC Curve

```{r}
#ROCR Curve
library(ROCR)
ROCRpred <- prediction(predict, test$pass_flag)
ROCRperf <- performance(ROCRpred, 'tpr','fpr')
plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2,1.7))
```


6. AUC Test data: 88.47%
```{r}
roc_obj <- roc(test$pass_flag, predict)
auc(roc_obj)
```



7. Measure Model Accuracy on test data:
```{r}

fitted.results <- ifelse(predict > 0.5,1,0) %>% as.factor()
cm<-confusionMatrix(data=fitted.results, 
  reference=as.factor(test$pass_flag))

Accuracy<-round(cm$overall[1],2)

```
    
    
        Hence the accuracy of this base model is :
        
        Accurary = (True Positives +True Negatives)/Total = `r round(Accuracy*100,2)` %
        

```{r}
# 7. Add probability to pass as a column in test data:
test$predicted <- predict
```
Accuracy on test data is 91%.

### Consolidation:
```{r}
modelled_dataset <-rbind(train, test) %>% arrange(predicted)
```

In the part analysis dataset, we would now list the part-feature & batch combinations which have low likelihood to pass the process test:
```{r}
modelled_dataset[which(modelled_dataset$predicted <0.3),]
```
\  

The above table shows the combinations which have high likelihood to fail. The predicted column shows the probability of passing the test and they range from 2% to 29% in the above table.


SHINY DECISION TOOL: interactive tool (to be built in future)



```{r,eval=FALSE, echo=TRUE}
## source code printed, but yet under process
shinyApp(
  
# Define UI for dataset viewer application
shinyUI <-pageWithSidebar(
  
  # Application title
  headerPanel("Select the batch inputs to check likelihood of passing the process quality test"),
  
  sidebarPanel(
                selectInput("select_Part_Desc", 
                            "Choose a Part Description:", 
                            choices = modelled_dataset$Part_Desc,
                            selected = "06_02_2015-035_PART:RE_T15E0065177_F:Fixture_D72__Purpose_In-Process"
                            
                ),
                
                selectInput("select_part_names", 
                            "Choose a Part Group:", 
                            choices = modelled_dataset$part_names,
                            selected = "RE_T15E0065177_F"
                            
                ),
                
                selectInput("select_date", 
                            "Input a Date and Time:", 
                            choices = modelled_dataset$Date,
                            selected = "2015-06-02 00:35:10 UTC"
                            
                ),
                
                
                selectInput("select_status", 
                            "Select the status:", 
                            choices = modelled_dataset$Status,
                            selected = "Purpose_In-Process"
                            
                ),
                
                
                selectInput("select_shift", 
                            "Choose the Shift:", 
                            choices = modelled_dataset$Shift,
                            selected = "Shift_C"
                            
                ),
                
                selectInput("select_trim", 
                            "Choose TRIM characters:", 
                            choices = modelled_dataset$Trim,
                            selected = "TCMM_05"
                            
                ),
                
                                
                selectInput("select_fix", 
                            "Choose Fixture type:", 
                            choices = modelled_dataset$Fixture_model,
                            selected = "Fixture_D72"
                            
                ),
                
                
                selectInput("select_machine", 
                            "Input the Machine type:", 
                            choices = modelled_dataset$Machine,
                            selected = "Machine_13"
                            
                ),
                
                
                selectInput("select_feature", 
                            "Choose the dimensional feature:", 
                            choices = modelled_dataset$dimensional_feature,
                            selected = "C0009DF073_SC07_DIA"
                            
                )
              ),
  

  mainPanel(
                verbatimTextOutput("Likelihood to Pass")

          )
),


# Define server logic required to summarize and view the selected dataset
shinyServer <-(function(input, output) {
  
  output$text <- renderText({
    "Likelihood to Pass is :" logit(input$select_Part_Desc,
           input$select_part_names,
           input$select_date,
           input$select_status,
           input$select_shift,
           input$select_trim,
           input$select_fix,
           input$select_machine,
           input$select_feature)
  })
  
}),
  
options = list(height = 500) 
  
)
```
